comgen-outline

### 2017-12-16 paper/case1-generics.Rmd
refresh to figures 2-4

```{r generics-prior-task, fig.cap:"Test"}
fig.priors.expt <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-bothStages.pdf", sep=""), scale = 1)
fig.priors.expt
```

@@

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features. Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution. A completely uniform distribution would be represented as the y = x line."}
load('../analysis/generics-priors-posteriorPredictives.Rdata')
ggplot(m.gen.endorse.priors.posteriorPredictive, 
           aes( x = prevalence, color = src, lty = src))+
      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    stat_ecdf(size = 1)+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  coord_fixed()+
    xlab("Feature-probability") +
    ylab("Cumulative probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

@@

for (p in example.generics.properties){
 priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
 inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
                                                   b = priorParams[["b"]]),
                               mix = priorParams[["mix"]]), 
                  utt = "generic")
 l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
 gen.listener.predictions <- bind_rows(
   gen.listener.predictions, 
   l0.rs %>% select(Parameter,value) %>% mutate(property = p)
   )
}

@@

m.gen.speakerBeliefs <- m.samp %>%
  filter(type == "targetPrevalence") %>%
  mutate(Sentence = paste(category, property)) %>%
  filter(Sentence %in% example.generics)

m.samp.prev.params <- m.samp %>%
    filter(type == "targetPrevalence") %>%
    mutate(Sentence = paste(category, property)) %>%
    filter(Sentence %in% example.generics) %>%
    mutate(parameter = paste(param, property, category, sep = "_")) %>%
    select(-param, -property, -category, -chain, -type) %>%
    group_by(parameter) %>%
    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
    ungroup() %>%
    separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
    group_by(category, property, iteration) %>%
    spread(parameter, val) %>%
    rowwise() %>%
    mutate(
      a = mean*sampleSize,
      b = (1-mean)*sampleSize,
      val = rbeta(n = 1, shape1 = a, shape2 = b)
      ) %>%
    ungroup()

@@

generics.endorsement.insets <- gen.inset.distributions %>%
  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
                                                  "state_Posterior",
                                                  "speakerBeliefs"),
                            labels = c("Listener Prior (Posterior given Silence)", 
                                       "Listener Posterior given Generic", 
                                       "Speaker Beliefs")),
         property = fct_relevel(property,
                                "have spots", "lay eggs","carry malaria", 
                                "are female", "dont eat people") ) %>%
  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
  facet_wrap(~property, nrow = 1)+
  geom_label_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F, color = "#2b83ba")+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Feature-probability") +
    ylab("Scaled probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())
```

```{r generics-endorsement-figure, fig.width=12, fig.height=9.5, fig.cap="Endorsing generalizations about categories. Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements. Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent feature-probability alone (lower left) and feature-probability + cue validity (lower right). Bottom: Five example feature-probability priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent feature-probability. These distributions are inferred using all three data sources from Expt. 1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}
grid.arrange(generics.endorsement.spectrum, 
             generics.endorsement.models,
             generics.endorsement.insets, ncol = 2,
             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
```

>>>>

```{r generics-prior-task, fig.cap="Prior elicitation task. A: Participants first generated animal names after seeing six example categories. B: One feature at a time, participants estimated the percentage of the category with the feature, for each category.", fig.height = 3}
fig.priors.expt.stage1 <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-stage1.jpeg", sep=""), scale = 1)
fig.priors.expt.stage2 <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-stage2.jpeg", sep=""), scale = 1)

plot_grid(fig.priors.expt.stage1, fig.priors.expt.stage2, labels = "AUTO")
```

@@

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features. Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution. A completely uniform distribution would be represented as the y = x line."}
load('../analysis/generics-priors-posteriorPredictives.Rdata')

gen.priors.densities <- ggplot(m.gen.endorse.priors.posteriorPredictive %>%
         filter(src == 'Data'), 
           aes( x = prevalence))+
           #aes( x = prevalence, color = src, lty = src))+
    geom_density(aes(y = ..scaled..), adjust = 1.3, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #stat_ecdf(size = 1)+
    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    #scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #coord_fixed()+
    xlab("") +
    ylab("Normalized probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

gen.priors.cdfs <-m.gen.endorse.priors.posteriorPredictive %>%
  mutate(src = factor(src, levels = c("Data", "Structured", "Unstructured"),
                      labels = c("Empirical distribution", 
                                 "Mixture of Betas",
                                 "Single Beta"))) %>%
ggplot(.,
           aes( x = prevalence, color = src, lty = src))+
    #geom_density(aes(y = ..scaled..), adjust = 1.3, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    stat_ecdf(size = 1)+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #coord_fixed()+
    xlab("Feature-probability") +
    ylab("Cumulative probability density")+
    theme(legend.title = element_blank(), legend.position = 'bottom')

gen.prior.fig1 <- gen.priors.densities +
  theme(plot.margin = unit(c(10,0,0,0), "pt")) 
gen.prior.fig2 <- gen.priors.cdfs  +
  theme(plot.margin = unit(c(10,0,6,0), "pt"))

plot_grid( 
 gen.prior.fig1, gen.prior.fig2,
           align = 'vh',
           labels = c("A", "B"),
           hjust = -1,
           nrow = 2,
           rel_heights = c(1, 1.2)
           #rel_widths = c(1.2, 3, 2)
           #rel_widths = c(1, 1.3)
           )
```

@@

# run interpreter model to generate "hypothetical intepretation" plots
for (p in example.generics.properties){
 priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
 inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
                                                   b = priorParams[["b"]]),
                               mix = priorParams[["mix"]]), 
                  utt = "generic")
 l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
 l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
 gen.listener.predictions <- bind_rows(
   gen.listener.predictions, 
   l0.rs.prior %>% select(value) %>% mutate(property = p, Parameter = "state_Prior"),
    l0.rs.posterior %>% select(value) %>% mutate(property = p, Parameter = "state_Posterior")
   )
}

@@

m.gen.speakerBeliefs <- m.samp %>%
  filter(type == "targetPrevalence") %>%
  mutate(Sentence = paste(category, property)) %>%
  filter(Sentence %in% example.generics) %>%
  mutate(property = factor(property))

# m.samp.prev.params <- m.samp %>%
#     filter(type == "targetPrevalence") %>%
#     mutate(Sentence = paste(category, property)) %>%
#     filter(Sentence %in% example.generics) %>%
#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
#     select(-param, -property, -category, -chain, -type) %>%
#     group_by(parameter) %>%
#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
#     ungroup() %>%
#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
#     group_by(category, property, iteration) %>%
#     spread(parameter, val) %>%
#     rowwise() %>%
#     mutate(
#       a = mean*sampleSize,
#       b = (1-mean)*sampleSize,
#       val = rbeta(n = 1, shape1 = a, shape2 = b)
#       ) %>%
#     ungroup()

@@

gen.inset.distributions.refactored <- gen.inset.distributions %>%
  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
                                                  "state_Posterior",
                                                  "speakerBeliefs"),
                            labels = c("Feature-probability Prior", 
                                       "Interpretation given generalization", 
                                       "Referent feature-probability")),
         property = fct_relevel(property,
                                "have spots", "lay eggs","carry malaria", 
                                "are female", "dont eat people") )

generics.endorsement.insets <- ggplot(gen.inset.distributions.refactored, 
                                      aes( x = value, fill = Parameter, 
                 color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
  facet_wrap(~property, nrow = 1)+
  geom_label_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F, color = "#2b83ba")+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Feature-probability") +
    ylab("Scaled probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())
```

```{r generics-endorsement-figure, fig.width = 11, fig.height=8.5, fig.cap="Endorsing generalizations about categories. Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements. Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent feature-probability alone (lower left) and feature-probability + cue validity (lower right). Bottom: Five example feature-probability priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent feature-probability. These distributions are inferred using all three data sources from Expt. 1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}

fig.gen.endorse.data <- generics.endorsement.spectrum +
  theme(plot.margin = unit(c(6,2,0,0), "pt")) #+ ggtitle("Feature-probability priors")
fig.gen.endorse.models <- generics.endorsement.models +
  theme(plot.margin = unit(c(6,2,0,0), "pt")) #+ ylab("")
fig.gen.endorse.priors <- generics.endorsement.insets +
  theme(plot.margin = unit(c(26,10,0,10), "pt"))

#+ 
    #theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
#p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))

fig.gen.endorse.toprow <- plot_grid(fig.gen.endorse.data,
                                     fig.gen.endorse.models, 
                                    # align = 'v',
                                    #  axis = 'l',
                                    labels = c("A", "B"),
                                    rel_widths = c(0.9, 1))

plot_grid(fig.gen.endorse.toprow,
          fig.gen.endorse.priors,
          labels = c("", "C"), nrow = 2, rel_heights = c(1.1, 0.6)
          )
# prow <- plot_grid( p1 + theme(legend.position="none"),
#            p2 + theme(legend.position="none"),
#            p3 + theme(legend.position="none"),
#            p4,
#            align = 'vh',
#            labels = c("A", "B", "C"),
#            hjust = -1,
#            #nrow = 1,
#            #rel_widths = c(1.2, 3, 2)
#            rel_widths = c(1.2, 3, 1.05, 1.7)
#            )

# grid.arrange(generics.endorsement.spectrum, 
#              generics.endorsement.models,
#              generics.endorsement.insets, ncol = 2,
#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))

### 2017-12-16 paper/comgen-paper.Rmd
refresh to figures 2-4

```{r}
priorNames <- c(
  "doesntEatPeople", #"uniformRare", 
  "isFemale", 
  "laysEggs", 
  #"eatsFood", 
  "barks",
  "carriesMalaria",
  "hasSpots"
 # "areSick"
  )
priorShapes <- list(
  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
)

@@

```{r cache = F}
fig.sims.priors <- ggplot(sims.priors, aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    ylab("Normalized probability density") +
    xlab("")+
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~., scales = 'free')+
    theme(strip.text.y = element_blank())
```

@@

```{r cache = F}
fig.sims.uncertain.threshold <- sims.uncertain.thresholds %>% mutate(PriorShape = factor(PriorShape, 
                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria"))) %>% 
                              ggplot(., aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("") +
    ylab("") +
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~., scales = 'free')+
    theme(strip.text.y = element_blank())#element_text(angle = 0, hjust = 0))
```

@@

s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
  geom_col(color = 'black')+
  # geom_label_repel(data = s1.simulations.relabeled, 
  #                  aes( label = example, fill = example),
  #                      color = 'white',
  #   box.padding = unit(0.0, "lines"),
  #   #point.padding = unit(1e-06, "lines"),
  #   segment.color = 'grey37')+
  scale_fill_solarized()+
  scale_x_continuous(limits = c(0, 1), 
                     breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 1))+
                     #labels = c("False", "True"))+
  coord_fixed(ratio = 1)+
  facet_grid(example~.)+
  guides(fill = F)+
  ylab("Endorsement")+xlab("Referent feature-probability")+
  theme(strip.text.y = element_text(angle = 0, hjust = 0), 
        axis.title.x = element_text(hjust = 0)
        #axis.title.y = element_text(vjust = 0)
        )
  #ylab("Endorsement model prediction")+
  #xlab("Hypothesized feature-probability")
#s1.simulations.scatter
```

```{r simulations, fig.cap = "Computational model behavior. A: Prior distributions over feature-probabilities for 6 example generalizations. B: Different fixed thresholds (columns) give rise to different posterior interpretations. C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors. D: Endorsement model predictions, assuming a particular referent feature-probability. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("Feature-probability priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,0), "pt"))

prow <- plot_grid( p1 + theme(legend.position="none"),
           p2 + theme(legend.position="none"),
           p3 + theme(legend.position="none"),
           p4,
           align = 'vh',
           labels = c("A", "B", "C", "D"),
           hjust = -1,
           nrow = 1,
           #rel_widths = c(1.2, 3, 2)
           rel_widths = c(1.2, 3, 1.1, 3)
           )
prow
```

>>>>

```{r simulationRuns}
priorNames <- c(
  "doesntEatPeople", #"uniformRare", 
  "isFemale", 
  "laysEggs", 
  #"eatsFood", 
  "barks",
  "carriesMalaria",
  "hasSpots"
 # "areSick"
  )
priorShapes <- list(
  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
)

@@

```{r cache = F}
fig.sims.priors <- ggplot(sims.priors, aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    ylab("Normalized probability density") +
    xlab("")+
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~., scales = 'free')+
    theme(strip.text.y = element_blank())
```

@@

```{r cache = F}
fig.sims.uncertain.threshold <- sims.uncertain.thresholds %>% mutate(PriorShape = factor(PriorShape, 
                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria"))) %>% 
                              ggplot(., aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("") +
    ylab("") +
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~., scales = 'free')+
    theme(strip.text.y = element_blank())#element_text(angle = 0, hjust = 0))
```

@@

s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
  geom_col(color = 'black')+
  # geom_label_repel(data = s1.simulations.relabeled, 
  #                  aes( label = example, fill = example),
  #                      color = 'white',
  #   box.padding = unit(0.0, "lines"),
  #   #point.padding = unit(1e-06, "lines"),
  #   segment.color = 'grey37')+
  scale_fill_solarized()+
  scale_x_continuous(limits = c(0, 1), 
                     breaks = c(0, 1))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 1),
                     labels = c("False", "True"))+
  #coord_fixed(ratio = 1)+
  coord_flip()+
  facet_grid(example~.)+
  guides(fill = F)+
  ylab("Endorsement")+xlab("Referent feature-probability")+
  theme(strip.text.y = element_text(angle = 0, hjust = 0)
        #axis.title.x = element_text(hjust = 0)
        #axis.title.y = element_text(vjust = 0)
        )
  #ylab("Endorsement model prediction")+
  #xlab("Hypothesized feature-probability")
```

```{r simulations, fig.cap = "Computational model behavior. A: Prior distributions over feature-probabilities for 6 example generalizations. B: Different fixed thresholds (columns) give rise to different posterior interpretations. C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors. D: Endorsement model predictions, assuming a particular referent feature-probability. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("Feature-probability priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,2,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))

prow <- plot_grid( p1 + theme(legend.position="none"),
           p2 + theme(legend.position="none"),
           p3 + theme(legend.position="none"),
           p4,
           align = 'vh',
           labels = c("A", "B", "C", "D"),
           hjust = -1,
           nrow = 1,
           #rel_widths = c(1.2, 3, 2)
           rel_widths = c(1.2, 3, 1.05, 1.7)
           )
prow
```
